Constructing a universe for the setoid model

### 2021-01-22 paper.tex
small change
reference to formalisation

This question was revisited and answered in Altenkirch et al. \cite{mpc19}. In
this paper, the authors define Setoid Type Theory (SeTT), an extension of
intensional Martin-L\"of type theory with constructs for setoid reasoning, where
funext and propext hold by definition. SeTT is based on the \emph{strict} setoid
model of Altenkirch\footnote{a \emph{strict} model is one where every equation
  holds definitionally}, which makes it possible to show consistency via a
syntactic translation. This is in contrast with other type theories based on the
setoid model, like Observational Type Theory \cite{alti:ott-conf}
and XTT \cite{xtt}, which instead rely on ETT for their justification. A major
property of SeTT is thus to illustrate how to bootstrap extensionality, by
translation into a small intensional core.

@@

The definition of the codes and predicate types follows that of the original
inductive-inductive type, and can be derived systematically from it. More
importantly, they can be defined without induction-induction, since although
$\textsf{Con}_0$ and $\textsf{Ty}_0$ are defined mutually, their sorts are not
indexed. \\
{\small
\begin{minipage}{0.4\textwidth}
\begin{align*}
  \bullet_0 &: \textsf{Con}_0 \\
  \blank,_0\blank &: \textsf{Con}_0 \to \textsf{Ty}_0 \to \textsf{Con}_0 \\
  \iota_0 &: \textsf{Con}_0 \to \textsf{Ty}_0 \\
  \Pi_0 &: \textsf{Con}_0 \to \textsf{Ty}_0 \to \textsf{Ty}_0 \to \textsf{Ty}_0 \hspace{2.8em} \\
\end{align*}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\vspace{-1.3em}
\begin{alignat*}{10}
  \bullet_1 &: \textsf{Con}_1\ \bullet_0 \\
  \blank,_1\blank &: \forall\{\GG_0\ A_0\} \to \textsf{Con}_1\ \GG_0 \to \textsf{Ty}_1\ \GG_0\ A_0 \\
  & \to \textsf{Con}_1\ (\GG_0 \,,_0 A_0) \\
  \iota_1 &: \forall\{\GG_0\} \to \textsf{Con}_1\ \GG_0 \to \textsf{Ty}_1\ \GG_0\ (\iota_0\ \GG_0) \\
  \Pi_1 &: \forall\{\GG_0\ A_0\ B_0\} \to \textsf{Con}_1\ \GG_0 \\
  & \to \textsf{Ty}_1\ \GG_0\ A_0 \to \textsf{Ty}_1\ (\GG_0\, ,_0 A_0)\ B_0 \\
  & \to \textsf{Ty}_1\ \GG_0\ (\Pi_0\ \GG_0\ A_0\ B_0)
\end{alignat*}
\end{minipage}}\vspace{0.4em}

>>>>

This question was revisited and answered in Altenkirch et al. \cite{mpc19}. In
this paper, the authors define Setoid Type Theory (SeTT), an extension of
intensional Martin-L\"of type theory with constructs for setoid reasoning, where
funext and propext hold by definition. SeTT is based on the \emph{strict} setoid
model of Altenkirch\footnote{A \emph{strict} model is one where every equation
  holds definitionally.}, which makes it possible to show consistency via a
syntactic translation. This is in contrast with other type theories based on the
setoid model, like Observational Type Theory \cite{alti:ott-conf}
and XTT \cite{xtt}, which instead rely on ETT for their justification. A major
property of SeTT is thus to illustrate how to bootstrap extensionality, by
translation into a small intensional core.

@@

The definition of the codes and predicate types follows that of the original
inductive-inductive type, and can be derived systematically from it. More
importantly, they can be defined without induction-induction, since although
$\textsf{Con}_0$ and $\textsf{Ty}_0$ are defined mutually, their sorts are not
indexed. \\

{\small
\begin{minipage}{0.4\textwidth}
\begin{align*}
  \bullet_0 &: \textsf{Con}_0 \\
  \blank,_0\blank &: \textsf{Con}_0 \to \textsf{Ty}_0 \to \textsf{Con}_0 \\
  \iota_0 &: \textsf{Con}_0 \to \textsf{Ty}_0 \\
  \Pi_0 &: \textsf{Con}_0 \to \textsf{Ty}_0 \to \textsf{Ty}_0 \to \textsf{Ty}_0 \hspace{2.8em} \\
\end{align*}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\vspace{-1.3em}
\begin{alignat*}{10}
  \bullet_1 &: \textsf{Con}_1\ \bullet_0 \\
  \blank,_1\blank &: \forall\{\GG_0\ A_0\} \to \textsf{Con}_1\ \GG_0 \to \textsf{Ty}_1\ \GG_0\ A_0 \\
  & \to \textsf{Con}_1\ (\GG_0 \,,_0 A_0) \\
  \iota_1 &: \forall\{\GG_0\} \to \textsf{Con}_1\ \GG_0 \to \textsf{Ty}_1\ \GG_0\ (\iota_0\ \GG_0) \\
  \Pi_1 &: \forall\{\GG_0\ A_0\ B_0\} \to \textsf{Con}_1\ \GG_0 \\
  & \to \textsf{Ty}_1\ \GG_0\ A_0 \to \textsf{Ty}_1\ (\GG_0\, ,_0 A_0)\ B_0 \\
  & \to \textsf{Ty}_1\ \GG_0\ (\Pi_0\ \GG_0\ A_0\ B_0)
\end{alignat*}
\end{minipage}}\vspace{0.4em}
